---
  title: "Key to a Productive Study Session"
  output: 
    flexdashboard::flex_dashboard:
      vertical_layout: fill
      theme:
        version: 4
        bootswatch: cerulean
      orientation: column
      storyboard: true
      self_contained: false
  date: "2023-03-17"
---
  
```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(plotly)
library(spotifyr)
library(compmus)
library(dplyr)
library(tidymodels)
library(ggdendro)
library(heatmaply)

lofi <- get_playlist_audio_features("", "1IESTA4eaoYhOAi5d0N5Kz?si=e499e373775e4f71")
s_classic <- get_playlist_audio_features("", "63PWggVCDaRoygnVT6zeot?si=69efc4e73940435b") 
non_lofi <- get_playlist_audio_features("", "66RrIu8zXbf3NiDX07e28Z?si=1cd6a16fe1c84826") 
futurefunk <- get_playlist_audio_features("", "5j5HRbB3Qy0GPGVbCrKP2G?si=91fbd0c8c6254fc6")
soft_lofi <-
  bind_rows(
    futurefunk |> mutate(category = "Future Funk"),
    non_lofi |> mutate(category = "Beast Mode"),
    s_classic |> mutate(category = "Soft Classical"),
    lofi |> mutate(category = "Study Lofi")
  ) 
chopin <-
  get_tidy_audio_analysis("40pgdwioxZSCUyCke0zzOp?si=c5c8c0e45dd54c76") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches) #'Nocturne in A-Flat Major, Op. 32, No. 2' by Chopin
ludovico <-
  get_tidy_audio_analysis("3weNRklVDqb4Rr5MhKBR3D?si=3723ad9ebb624e86") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches) #Nuvole Bianche by Ludovico Einaudi
blackpink <-
  get_tidy_audio_analysis("0skYUMpS0AcbpjcGsAbRGj?si=1845018d70214865") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
dualipa <-
  get_tidy_audio_analysis("5nujrmhLynf4yMoMtj8AQF?si=7edf27c3177b417f") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
futurefunk1 <-
  get_tidy_audio_analysis("6lSrgTxyF9XgyLuNByH7Vm?si=e481dedf14de48f0") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
futurefunk2 <-
  get_tidy_audio_analysis("2sj2K4VaNNkW17K1yhgrAm?si=9a95d533438b4ee5") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
lofi1 <-
  get_tidy_audio_analysis("5yzk0dn1DmFcTkon5JrtTc?si=61052cc7cd0741dd") |> # Forgotten Past by Dosi, Wishes and Dreams
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
lofi2 <-
  get_tidy_audio_analysis("6y3y1s6eiTYsLEajJGbCkj?si=2a95b480bd31415c") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches) # Cadenza by Lucid Keys, Mondo Loops
lofi3 <-
  get_tidy_audio_analysis("0UCJtleZmlwpicJkmrys4a?si=8172fd17c8834ca2") |># convo by SNUG
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
```

Cross-playlist comparison {data-navmenu=Visualisation}
=========================================

Column{data-width=700}
-----------------------------------------

### Cross-playlist comparison

```{r}
chart1 <- soft_lofi |>                    # Soft vs. Lofi.
  mutate(
    instrumentalness = ifelse(instrumentalness == 0, "Low", "High")
  ) |>
  ggplot(                     # Set up the plot.
    aes(
      x = acousticness,
      y = energy,
      size = loudness,
      colour = instrumentalness
    )
  ) +
  geom_point() +              # Scatter plot.
  geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  facet_wrap(~ category) +    # Separate charts per playlist.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   # Use grid-lines for quadrants only.
    minor_breaks = NULL     # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        # Use the Color Brewer to choose a palette.
    type = "qual",            # Qualitative set.
    palette = "Set1"        # Name of the palette is 'Paired'.
  ) +
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud.            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Acousticness",
    y = "Energy",
    colour = "instrumentalness"
  )

ggplotly(chart1)

```

***

  In the plot we are contrasting and comparing three playlists. First one is called "Beast Mode" with almost 10,000,000 likes on Spotify and 200 songs. Second goes the "Soft Classical Study" with 1,000 likes and 138 songs. Third goes the "Study Lofi" playlist with 7,000,000 likes and 500 songs. After several experiments and combinations of features the most interesting picture came up with accousticness on x-axis and energy on y-axis. Simultaneously we are looking at the size and color of the dots to see the level of loudness and instrumentalness, respectively. The obvious observations we can make are that first and foremost, study playlist tend to consist of songs with lower energy and higher accousticness. The other two conclusions are pretty much all of the songs in study playlists have high instrumentalness. Last conclusion is that loudness level is low in study playlists and combination of all levels can be observed for the "Beast Mode".

Column{data-width=300}
-----------------------------------------
Description 
  

Within playlist comparison (chroma features) {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### LOFI📚

```{r}
chart2 <- compmus_long_distance(
  lofi1 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  lofi2 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Forgotten Past by Dosi, Wishes and Dreams", y = "Lofi2") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart2)
chart2
```

***
"embeded link to be added"
  
### CLASSICAL🎻

```{r}
chart2 <- compmus_long_distance(
  chopin |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  ludovico |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "'Nocturne in B Major, Op. 62, No. 1' by Chopin", y = "'Nuvole Bianche' by Ludovico Einaudi") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart2)
chart2
```

***
"embeded link to be added"


### WORKOUT🏆

```{r}
chart2 <- compmus_long_distance(
  blackpink |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  dualipa |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Pink Venom by Blackpink", y = "Levitating by Dua Lipa") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart2)
chart2
```

***
"embeded link to be added"

### FUTURE FUNK🎇

```{r}
chart2 <- compmus_long_distance(
  futurefunk1 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  futurefunk2 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "I Chose Wrong by Chance", y = "Highway Night Lights by Bionsen") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart2)
chart2
```

***
"embeded link to be added"

Column{data-width=300}
-----------------------------------------

Description


Cross-playlist comparison (study playlist vs. workout playlist) {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### LOFI📚 vs. CLASSICAL🎻

```{r}
chart3 <- compmus_long_distance(
  lofi1 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  chopin |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "convo by SNUG", y = "Nocturne B. Major by Chopin") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart3)
chart3
```

***
"embeded link to be added"

### LOFI📚 vs. FUTURE FUNK🎇

```{r}
chart3 <- compmus_long_distance(
  lofi1 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  futurefunk1 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "convo by SNUG", y = "I Chose Wrong by Chance") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart3)
chart3
```

***
"embeded link to be added"

### CLASSICAL🎻 vs. WORKOUT🏆

```{r}
chart3 <- compmus_long_distance(
  chopin |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  blackpink |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Nocturne B. Major by Chopin", y = "Pink Venom by Blankpink") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart3)
chart3
```

***
"embeded link to be added"

### WORKOUT🏆 vs. FUTURE FUNK🎇

```{r}
chart3 <- compmus_long_distance(
  futurefunk1 |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  blackpink |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "I Chose Wrong by Chance", y = "Pink Venom by Blankpink") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart3)
chart3
```

***
"embeded link to be added"

Column{data-width=300}
-----------------------------------------

Description 


Cepstrograms {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### LOFI📚

```{r}
lofi1 <-
  get_tidy_audio_analysis("5yzk0dn1DmFcTkon5JrtTc?si=61052cc7cd0741dd") |>  # Forgotten Past by Dosi, Wishes and Dreams
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

lofi2 <-
  get_tidy_audio_analysis("6y3y1s6eiTYsLEajJGbCkj?si=2a95b480bd31415c") |> # Cadenza by Lucid Keys, Mondo Loops
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

lofi3 <-
  get_tidy_audio_analysis("0UCJtleZmlwpicJkmrys4a?si=8172fd17c8834ca2") |> # convo by SNUG
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bind_rows(
lofi1 |>
  compmus_gather_timbre() |>
  mutate(type = "Lofi 1"),
lofi2 |>
  compmus_gather_timbre() |>
  mutate(type = "Lofi 2"),
lofi3 |>
  compmus_gather_timbre() |>
  mutate(type = "Lofi 3")
) |>
  mutate() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  facet_wrap(~type) +
  scale_fill_viridis_c() +
  theme_classic() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude")
```

***

Cepstrograms breakdown of the lofi beat by less.people from research playlist#1.
"embeded link to be added"


### CLASSICAL🎻

```{r}
chopin <-
  get_tidy_audio_analysis("40pgdwioxZSCUyCke0zzOp?si=c5c8c0e45dd54c76") |> # "Nocturne in A-Flat Major, Op. 32, No.2" by Chopin
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

ludovico <-
  get_tidy_audio_analysis("3weNRklVDqb4Rr5MhKBR3D?si=c1f8a23072464783") |> # Nuvole Bianche by Ludovico Einaudi
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
joep <-
  get_tidy_audio_analysis("55U56qbqS1g1PaeyIznUjr?si=7da1df14c38c4a3f") |> # Midwayer by Joep Beving
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bind_rows(
chopin |>
  compmus_gather_timbre() |>
  mutate(type = "Nocturne by Chopin"),
ludovico |>
  compmus_gather_timbre() |>
  mutate(type = "Nuvole Bianche by Ludovico Einaudi"),
joep |>
  compmus_gather_timbre() |>
  mutate(type = "Midwayer by Joep Beving")
) |>
  mutate() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  facet_wrap(~type) +
  scale_fill_viridis_c() +
  theme_classic() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude")
```

***

Cepstrograms breakdown of the soft classic song by Chopin from research playlist#2.
"embeded link to be added"

### WORKOUT🏆

```{r}
blackpink <-
  get_tidy_audio_analysis("0skYUMpS0AcbpjcGsAbRGj?si=1845018d70214865") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
dualipa <-
  get_tidy_audio_analysis("5nujrmhLynf4yMoMtj8AQF?si=bed60c3fbaa548ee") |> # Nuvole Bianche by Ludovico Einaudi
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
lilnasx <-
  get_tidy_audio_analysis("27NovPIUIRrOZoCHxABJwK?si=937f39f001ac48e8") |> # Midwayer by Joep Beving
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bind_rows(
blackpink |>
  compmus_gather_timbre() |>
  mutate(type = "Pink Venom by Blackpink"),
dualipa |>
  compmus_gather_timbre() |>
  mutate(type = "Levitating by Dua Lipa"),
lilnasx |>
  compmus_gather_timbre() |>
  mutate(type = "Industry Baby by Lil Nas X and Jack Harlow")
) |>
  mutate() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  facet_wrap(~type) +
  scale_fill_viridis_c() +
  theme_classic() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude")
```

***

Cepstrograms breakdown of the pop song "Pink Venom" by Blackpink from research playlist#3.
"embeded link to be added"

### FUTURE FUNK🎇

```{r}
futurefunk1 <-
  get_tidy_audio_analysis("6lSrgTxyF9XgyLuNByH7Vm?si=0131824e2ffa4572") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
futurefunk2 <-
  get_tidy_audio_analysis("2sj2K4VaNNkW17K1yhgrAm?si=e62a0008430c481a") |> # Highway Night Lights by Bionsen
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
futurefunk3 <-
  get_tidy_audio_analysis("5raJYLpnYe0fA9aaN5oBv8?si=8e462d63fcf4444d") |> # Feeling different Ajotabeats
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bind_rows(
futurefunk1 |>
  compmus_gather_timbre() |>
  mutate(type = "I Chose Wrong by Chance"),
futurefunk2 |>
  compmus_gather_timbre() |>
  mutate(type = "Highway Night Lights by Bionsen"),
futurefunk3 |>
  compmus_gather_timbre() |>
  mutate(type = "Feeling Different by Ajotabeats")
) |>
  mutate() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  facet_wrap(~type) +
  scale_fill_viridis_c() +
  theme_classic() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude")
```

***

Cepstrograms breakdown of the pop song "Pink Venom" by Blackpink from research playlist#3.
"embeded link to be added"

Column{data-width=300}
-----------------------------------------

Description 

Self Similarity Matrix {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### LOFI📚

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)

bind_rows(
  lofi1 |>
    compmus_self_similarity(pitches, "aitchison") |>
    mutate(d = d / max(d), type = "Chroma"),
  lofi1 |>
    compmus_self_similarity(timbre, "euclidean") |>
    mutate(d = d / max(d), type = "Timbre")
) |>
  mutate() |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

***

This is chroma and timbre cross analysis of lofi beat piece Forgotten Past by Dosi, Wishes and Dreams
"embeded link to be added"

### CLASSICAL🎻

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)

bind_rows(
  chopin |>
    compmus_self_similarity(pitches, "aitchison") |>
    mutate(d = d / max(d), type = "Chroma"),
  chopin |>
    compmus_self_similarity(timbre, "euclidean") |>
    mutate(d = d / max(d), type = "Timbre")
) |>
  mutate() |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

***

This is chroma and timbre cross analysis of soft classical piece "Nocturne in A-Flat Major Op. 32, No.2" by Chopin.
"embeded link to be added"

### WORKOUT🏆

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)

bind_rows(
  blackpink |>
    compmus_self_similarity(pitches, "aitchison") |>
    mutate(d = d / max(d), type = "Chroma"),
  blackpink |>
    compmus_self_similarity(timbre, "euclidean") |>
    mutate(d = d / max(d), type = "Timbre")
) |>
  mutate() |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

***

This is chroma and timbre cross analysis of Pink Venom by Blackpink. 
"embeded link to be added"


### FUTURE FUNK🎇

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)

bind_rows(
  futurefunk1 |>
    compmus_self_similarity(pitches, "aitchison") |>
    mutate(d = d / max(d), type = "Chroma"),
  futurefunk1 |>
    compmus_self_similarity(timbre, "euclidean") |>
    mutate(d = d / max(d), type = "Timbre")
) |>
  mutate() |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

***

This is chroma and timbre cross analysis of Pink Venom by Blackpink. 
"embeded link to be added"

Column{data-width=300}
-----------------------------------------

Description

Chordograms {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### LOFI📚

```{r}
circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )

lofi1 |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

***

This is chroma and timbre cross analysis of lofi beat piece Forgotten Past by Dosi, Wishes and Dreams
"embeded link to be added"

### CLASSICAL🎻

```{r, echo=FALSE}
chopin |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

***

This is chroma and timbre cross analysis of soft classical piece "Nocturne in A-Flat Major Op. 32, No.2" by Chopin.
"embeded link to be added"

### WORKOUT🏆

```{r}
blackpink |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

***

This is chroma and timbre cross analysis of Pink Venom by Blackpink. 
"embeded link to be added"

###  FUTURE FUNK🎇

```{r}
futurefunk1 |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

***

This is chroma and timbre cross analysis of Pink Venom by Blackpink. 
"embeded link to be added"

Column{data-width=300}
-----------------------------------------

Description 


Clustering - Lofi {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### Single

```{r}
lofi <-
  get_playlist_audio_features("", "1IESTA4eaoYhOAi5d0N5Kz?si=e499e373775e4f71") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

lofi_study_s <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

study_dist_s <- dist(lofi_study_s, method = "euclidean")

study_dist_s |> 
  hclust(method = "single") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  lofi_study_s,
  hclustfun = hclust,
  hclust_method = "single",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Average

```{r}
lofi <-
  get_playlist_audio_features("", "1IESTA4eaoYhOAi5d0N5Kz?si=e499e373775e4f71") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

lofi_study_a <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

study_dist_a <- dist(lofi_study_a, method = "euclidean")

study_dist_a |> 
  hclust(method = "average") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  lofi_study_a,
  hclustfun = hclust,
  hclust_method = "average",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Complete

```{r}
lofi <-
  get_playlist_audio_features("", "1IESTA4eaoYhOAi5d0N5Kz?si=e499e373775e4f71") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

lofi_study_c <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

study_dist_c <- dist(lofi_study_c, method = "euclidean")

study_dist_c |> 
  hclust(method = "complete") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  lofi_study_c,
  hclustfun = hclust,
  hclust_method = "complete",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

Column{data_width = 300}
-----------------------------------------
Description


Clustering - Classical {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### Single

```{r}
soft_classical <-
  get_playlist_audio_features("", "63PWggVCDaRoygnVT6zeot?si=69efc4e73940435b") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

soft_study_s <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

soft_dist_s <- dist(soft_study_s, method = "euclidean")

soft_dist_s |> 
  hclust(method = "single") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  soft_study_s,
  hclustfun = hclust,
  hclust_method = "single",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Average

```{r}
soft_classical <-
  get_playlist_audio_features("", "63PWggVCDaRoygnVT6zeot?si=69efc4e73940435b") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

soft_study_a <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

soft_dist_a <- dist(soft_study_a, method = "euclidean")

soft_dist_a |> 
  hclust(method = "average") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  soft_study_a,
  hclustfun = hclust,
  hclust_method = "average",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Complete

```{r}
soft_classical <-
  get_playlist_audio_features("", "63PWggVCDaRoygnVT6zeot?si=69efc4e73940435b") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

soft_study_c <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

soft_dist_c <- dist(soft_study_c, method = "euclidean")

soft_dist_c |> 
  hclust(method = "complete") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  soft_study_c,
  hclustfun = hclust,
  hclust_method = "complete",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

Column{data-width=300}
-----------------------------------------
Description

Clustering - Workout {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### Single

```{r}
workout <-
  get_playlist_audio_features("", "5j5HRbB3Qy0GPGVbCrKP2G?si=dd861654a8ae4ff2") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

workout_study_s <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

workout_dist_s <- dist(workout_study_s, method = "euclidean")

workout_dist_s |> 
  hclust(method = "single") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  workout_study_s,
  hclustfun = hclust,
  hclust_method = "single",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Average

```{r}
workout <-
  get_playlist_audio_features("", "5j5HRbB3Qy0GPGVbCrKP2G?si=dd861654a8ae4ff2") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

workout_study_a <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

workout_dist_a <- dist(workout_study_a, method = "euclidean")

workout_dist_a |> 
  hclust(method = "average") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  workout_study_a,
  hclustfun = hclust,
  hclust_method = "average",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Complete

```{r}
workout <-
  get_playlist_audio_features("", "5j5HRbB3Qy0GPGVbCrKP2G?si=dd861654a8ae4ff2") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

workout_study_c <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

workout_dist_c <- dist(workout_study_c, method = "euclidean")

workout_dist_c |> 
  hclust(method = "complete") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  workout_study_c,
  hclustfun = hclust,
  hclust_method = "complete",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

Column{data-width=300}
-----------------------------------------

Description

Clustering - Future Funk {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### Single

```{r}
futurefunk <-
  get_playlist_audio_features("", "5j5HRbB3Qy0GPGVbCrKP2G?si=91fbd0c8c6254fc6") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

future_study_s <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

future_dist_s <- dist(future_study_s, method = "euclidean")

future_dist_s |> 
  hclust(method = "single") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  future_study_s,
  hclustfun = hclust,
  hclust_method = "single",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Average

```{r}
futurefunk <-
  get_playlist_audio_features("", "5j5HRbB3Qy0GPGVbCrKP2G?si=91fbd0c8c6254fc6") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

future_study_a <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

future_dist_a <- dist(future_study_a, method = "euclidean")

future_dist_a |> 
  hclust(method = "average") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  future_study_a,
  hclustfun = hclust,
  hclust_method = "average",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

### Complete

```{r}
futurefunk <-
  get_playlist_audio_features("", "5j5HRbB3Qy0GPGVbCrKP2G?si=91fbd0c8c6254fc6") |>
  slice(1:50) |>
  add_audio_analysis() |>
  mutate(
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

future_study_c <-
  recipe(
    track.name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = lofi
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  # step_range(all_predictors()) |> 
  prep(lofi |> mutate(track.name = str_trunc(track.name, 20))) |>
  juice() |>
  column_to_rownames("track.name")

future_dist_c <- dist(future_study_c, method = "euclidean")

future_dist_c |> 
  hclust(method = "complete") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()

heatmaply(
  future_study_c,
  hclustfun = hclust,
  hclust_method = "complete",  # Change for single, average, or complete linkage.
  dist_method = "euclidean"
)
```

Column{data-width=300}
-----------------------------------------
Description

Track Level Summaries {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### Track Level Summaries 1

```{r}
lofi <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "1IESTA4eaoYhOAi5d0N5Kz?si=e499e373775e4f71"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
soft_classical <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "63PWggVCDaRoygnVT6zeot?si=69efc4e73940435b"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
workout <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "66RrIu8zXbf3NiDX07e28Z?si=1cd6a16fe1c84826"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
futurefunk <- get_playlist_audio_features("thesoundsofspotify","5j5HRbB3Qy0GPGVbCrKP2G?si=bf6a2493733c40c5") |>
  slice(1:30) |>
  add_audio_analysis()
study <-
  lofi |>
  mutate(genre = "Lofi") |>
  bind_rows(workout |> mutate(genre = "Workout"), soft_classical |> mutate(genre = "Soft Classical"), futurefunk |> mutate(genre = "Future Funk"))
study |>
  mutate(
    sections =
      map(
        sections,                                    # sections or segments
        summarise_at,
        vars(tempo, loudness, duration),             # features of interest
        list(section_mean = mean, section_sd = sd)   # aggregation functions
      )
  ) |>
  unnest(sections) |>
  ggplot(
    aes(
      x = tempo,
      y = tempo_section_sd,
      colour = genre,
      alpha = loudness
    )
  ) +
  geom_point(aes(size = duration / 60)) +
  geom_rug() +
  theme_minimal() +
  ylim(0, 5) +
  labs(
    x = "Mean Tempo (bpm)",
    y = "SD Tempo",
    colour = "Genre",
    size = "Duration (min)",
    alpha = "Volume (dBFS)"
  )

```

***

"embeded link to be added"

### Track Level Summaries 2

```{r}
chart4 <- study |>
  mutate(
    timbre =
      map(
        segments,
        compmus_summarise,
        timbre,
        method = "mean"
      )
  ) |>
  select(genre, timbre) |>
  compmus_gather_timbre() |>
  ggplot(aes(x = basis, y = value, fill = genre)) +
  geom_violin() +
  scale_fill_viridis_d() +
  labs(x = "Spotify Timbre Coefficients", y = "", fill = "Genre")

ggplotly(chart4)
```

***

"embeded link to be added"

Column{data-width=300}
-----------------------------------------
Description

Tempograms {data-navmenu=Visualisation}
=========================================

Column{data-width=700 .tabset}
-----------------------------------------

### LOFI📚

```{r}
lofi1 <- get_tidy_audio_analysis("5yzk0dn1DmFcTkon5JrtTc?si=61052cc7cd0741dd")   # Forgotten Past by Dosi, Wishes and Dreams
lofi1 |>
  tempogram(window_size = 8, hop_size = 1, cyclic = FALSE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

### CLASSICAL🎻

```{r}
chopin <- get_tidy_audio_analysis("40pgdwioxZSCUyCke0zzOp?si=c5c8c0e45dd54c76")   # Forgotten Past by Dosi, Wishes and Dreams
chopin |>
  tempogram(window_size = 8, hop_size = 1, cyclic = FALSE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

### WORKOUT🏆 

```{r}
blackpink <- get_tidy_audio_analysis("0skYUMpS0AcbpjcGsAbRGj?si=1845018d70214865")
blackpink |>
  tempogram(window_size = 8, hop_size = 1, cyclic = FALSE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```


### FUTURE FUNK🎇

```{r}
futurefunk1 <- get_tidy_audio_analysis("62jdesXaWtAVtMK75zJn4h?si=d40559b27bd7487a") # "Flashback' by Rhodes Rodosu
futurefunk1 |>
  tempogram(window_size = 8, hop_size = 1, cyclic = FALSE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

Column{data-width=300}
-----------------------------------------
Description 

Introduction{.storyboard data-navmenu=Introduction}
=========================================
  
### What features recipe goes into making the best study playlist?
  
```{r}

```

Study playlist can play an important role in the productivity level of any study session. While studying together with friends we ended up in situation where we had to listen to our individual playlists in headphones, because each of our taste in study music was very different. Therefore the first question I want to look into is "What makes any music or song a study-friendly option?". Does it involve its slow rhytm, low dancebility, low energy, low dancebility, yet the most important question I want to figure out is the level of accousticness and instrumentalness across various types of study playlists. My main research question is what combination of the main features classify the music into study friendly. It will be possible to compare the opposite of study music, for example, workout or party playlist and contrast it to study music. 

### Focus playlists 

"embeded link to be added"

Conclusion{.storyboard}
=========================================
  
### Conclusion 
  
```{r}

```
