---
  title: "Storyboard"
  output: 
    flexdashboard::flex_dashboard:
      vertical_layout: fill
      theme: journal 
      orientation: column
  date: "2023-02-26"
---
  
```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(plotly)
library(spotifyr)
library(compmus)
library(dplyr)
lofi <- get_playlist_audio_features("", "0vvXsWCC9xrXsKd4FyS8kM?si=59987a21511a4fc1")
s_classic <- get_playlist_audio_features("", "6d7BJsiKHny0PHvgn62pBU?si=3cd9d8cce4d145c5") 
non_lofi <- get_playlist_audio_features("", "37i9dQZF1DX76Wlfdnj7AP?si=8263b5c28feb41d7") 
soft_lofi <-
  bind_rows(
    lofi |> mutate(category = "Study Lofi"),
    s_classic |> mutate(category = "Soft Classical"),
    non_lofi |> mutate(category = "Beast Mode")
  ) 
chopin <-
  get_tidy_audio_analysis("40pgdwioxZSCUyCke0zzOp?si=e4773e8cdc504b60") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
una <-
  get_tidy_audio_analysis("3weNRklVDqb4Rr5MhKBR3D?si=3723ad9ebb624e86") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

blackpink <-
  get_tidy_audio_analysis("0skYUMpS0AcbpjcGsAbRGj?si=1845018d70214865") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

```
Visualisation {.storyboard}
=========================================

### Cepstrograms

```{r}
chopin <-
  get_tidy_audio_analysis("40pgdwioxZSCUyCke0zzOp?si=e4773e8cdc504b60") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

chopin |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = "Nocturne by Chopin")
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

lofi <-
  get_tidy_audio_analysis("5jDr57ExdEW04Zjcsb4XKK?si=b51774123a904b5f") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

lofi |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

blackpink <-
  get_tidy_audio_analysis("0skYUMpS0AcbpjcGsAbRGj?si=1845018d70214865") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

blackpink |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Pink Venom by Blankpink')
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()
```

### Self-similarity matrix

```{r}
chopin |>
  compmus_self_similarity(pitches, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d, title(main = 'Chroma')
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")

chopin |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d, title(main = 'Timbre')
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")

```

### Cross-playlist comparison
  
```{r}
chart1 <- soft_lofi |>                    # Soft vs. Lofi.
  mutate(
    instrumentalness = ifelse(instrumentalness == 0, "Low", "High")
  ) |>
  ggplot(                     # Set up the plot.
    aes(
      x = acousticness,
      y = energy,
      size = loudness,
      colour = instrumentalness
    )
  ) +
  geom_point() +              # Scatter plot.
  geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  facet_wrap(~ category) +    # Separate charts per playlist.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   # Use grid-lines for quadrants only.
    minor_breaks = NULL     # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        # Use the Color Brewer to choose a palette.
    type = "qual",            # Qualitative set.
    palette = "Set1"        # Name of the palette is 'Paired'.
  ) +
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud.            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Acousticness",
    y = "Energy",
    colour = "instrumentalness"
  )

ggplotly(chart1)

```
***
  In the plot we are contrasting and comparing three playlists. First one is called "Beast Mode" with almost 10,000,000 likes on Spotify and 200 songs. Second goes the "Soft Classical Study" with 1,000 likes and 138 songs. Third goes the "Study Lofi" playlist with 7,000,000 likes and 500 songs. After several experiments and combinations of features the most interesting picture came up with accousticness on x-axis and energy on y-axis. Simultaneously we are looking at the size and color of the dots to see the level of loudness and instrumentalness, respectively. The obvious observations we can make are that first and foremost, study playlist tend to consist of songs with lower energy and higher accousticness. The other two conclusions are pretty much all of the songs in study playlists have high instrumentalness. Last conclusion is that loudness level is low in study playlists and combination of all levels can be observed for the "Beast Mode".

  
### Within playlist comparison (chroma features)

```{r}
chart2 <- compmus_long_distance(
  chopin |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  una |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "'Nocturne in B Major, Op. 62, No. 1' by Chopin", y = "'Nuvole Bianche' by Una Mattina") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart2)
chart2
```


### Cross-playlist comparison (study playlist vs. workout playlist)

```{r}
chart3 <- compmus_long_distance(
  chopin |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  blackpink |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Nocturne B. Major by Chopin", y = "Pink Venom by Blankpink") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart3)
chart3
```


Introduction {.storyboard}
=========================================
  
### What features recipe goes into making the best study playlist?
  
```{r}

```

Study playlist can play an important role in the productivity level of any study session. While studying together with friends we ended up in situation where we had to listen to our individual playlists in headphones, because each of our taste in study music was very different. Therefore the first question I want to look into is "What makes any music or song a study-friendly option?". Does it involve its slow rhytm, low dancebility, low energy, low dancebility, yet the most important question I want to figure out is the level of accousticness and instrumentalness across various types of study playlists. My main research question is what combination of the main features classify the music into study friendly. It will be possible to compare the opposite of study music, for example, workout or party playlist and contrast it to study music. 


Conclusion {.storyboard}
=========================================
  
### Conclusion {.storyboard}
  
```{r}

```
