---
  title: "Storyboard"
  output: 
    flexdashboard::flex_dashboard:
      vertical_layout: fill
      theme:
        version: 4
        bootswatch: minty
      orientation: column
      storyboard: true
      self_contained: false
  date: "2023-02-26"
---
  
```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(plotly)
library(spotifyr)
library(compmus)
library(dplyr)
lofi <- get_playlist_audio_features("", "0vvXsWCC9xrXsKd4FyS8kM?si=59987a21511a4fc1")
s_classic <- get_playlist_audio_features("", "6d7BJsiKHny0PHvgn62pBU?si=3cd9d8cce4d145c5") 
non_lofi <- get_playlist_audio_features("", "37i9dQZF1DX76Wlfdnj7AP?si=8263b5c28feb41d7") 
soft_lofi <-
  bind_rows(
    lofi |> mutate(category = "Study Lofi"),
    s_classic |> mutate(category = "Soft Classical"),
    non_lofi |> mutate(category = "Beast Mode")
  ) 
chopin <-
  get_tidy_audio_analysis("40pgdwioxZSCUyCke0zzOp?si=e4773e8cdc504b60") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
ludovico <-
  get_tidy_audio_analysis("3weNRklVDqb4Rr5MhKBR3D?si=3723ad9ebb624e86") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

blackpink <-
  get_tidy_audio_analysis("0skYUMpS0AcbpjcGsAbRGj?si=1845018d70214865") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
lofi1 <-
  get_tidy_audio_analysis("2nPFhADlsEdtUenU1PgHoS?si=b6d1338822b74961") # Juneberry by Lawrence Walther
lofi2 <-
  get_tidy_audio_analysis("6y3y1s6eiTYsLEajJGbCkj?si=2a95b480bd31415c") # Cadenza by Lucid Keys, Mondo Loops
lofi3 <-
  get_tidy_audio_analysis("0UCJtleZmlwpicJkmrys4a?si=8172fd17c8834ca2")


```

Cross-playlist comparison {.storyboard data-navmenu=Visualisation}
=========================================

### Cross-playlist comparison

```{r}
chart1 <- soft_lofi |>                    # Soft vs. Lofi.
  mutate(
    instrumentalness = ifelse(instrumentalness == 0, "Low", "High")
  ) |>
  ggplot(                     # Set up the plot.
    aes(
      x = acousticness,
      y = energy,
      size = loudness,
      colour = instrumentalness
    )
  ) +
  geom_point() +              # Scatter plot.
  geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  facet_wrap(~ category) +    # Separate charts per playlist.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   # Use grid-lines for quadrants only.
    minor_breaks = NULL     # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        # Use the Color Brewer to choose a palette.
    type = "qual",            # Qualitative set.
    palette = "Set1"        # Name of the palette is 'Paired'.
  ) +
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud.            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Acousticness",
    y = "Energy",
    colour = "instrumentalness"
  )

ggplotly(chart1)

```

***

  In the plot we are contrasting and comparing three playlists. First one is called "Beast Mode" with almost 10,000,000 likes on Spotify and 200 songs. Second goes the "Soft Classical Study" with 1,000 likes and 138 songs. Third goes the "Study Lofi" playlist with 7,000,000 likes and 500 songs. After several experiments and combinations of features the most interesting picture came up with accousticness on x-axis and energy on y-axis. Simultaneously we are looking at the size and color of the dots to see the level of loudness and instrumentalness, respectively. The obvious observations we can make are that first and foremost, study playlist tend to consist of songs with lower energy and higher accousticness. The other two conclusions are pretty much all of the songs in study playlists have high instrumentalness. Last conclusion is that loudness level is low in study playlists and combination of all levels can be observed for the "Beast Mode".
  

Within playlist comparison (chroma features) {.storyboard data-navmenu=Visualisation}
=========================================
  
### Within playlist comparison (chroma features) 

```{r}
chart2 <- compmus_long_distance(
  chopin |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  ludovico |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "'Nocturne in B Major, Op. 62, No. 1' by Chopin", y = "'Nuvole Bianche' by Ludovico Einaudi") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart2)
chart2
```

Cross-playlist comparison (study playlist vs. workout playlist) {.storyboard data-navmenu=Visualisation}
=========================================

### Cross-playlist comparison (study playlist vs. workout playlist) 

```{r}
chart3 <- compmus_long_distance(
  chopin |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  blackpink |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Nocturne B. Major by Chopin", y = "Pink Venom by Blankpink") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
# ggplotly(chart3)
chart3
```

Cepstrograms {.storyboard data-navmenu=Visualisation}
=========================================

### Lofi

```{r}
lofi1 <-
  get_tidy_audio_analysis("2nPFhADlsEdtUenU1PgHoS?si=b6d1338822b74961") |> # Juneberry by Lawrence Walther
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

lofi2 <-
  get_tidy_audio_analysis("6y3y1s6eiTYsLEajJGbCkj?si=2a95b480bd31415c") |> # Cadenza by Lucid Keys, Mondo Loops
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

lofi3 <-
  get_tidy_audio_analysis("0UCJtleZmlwpicJkmrys4a?si=8172fd17c8834ca2") |> # convo by SNUG
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bind_rows(
lofi1 |>
  compmus_gather_timbre() |>
  mutate(type = "Lofi 1"),
lofi2 |>
  compmus_gather_timbre() |>
  mutate(type = "Lofi 2"),
lofi3 |>
  compmus_gather_timbre() |>
  mutate(type = "Lofi 3")
) |>
  mutate() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  facet_wrap(~type) +
  scale_fill_viridis_c() +
  theme_classic() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude")
```

***

Cepstrograms breakdown of the lofi beat by less.people from research playlist#1.

### Soft Classical

```{r}
chopin <-
  get_tidy_audio_analysis("40pgdwioxZSCUyCke0zzOp?si=178d1c0ce41b4c99") |> # Nocturne by Chopin
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

ludovico <-
  get_tidy_audio_analysis("3weNRklVDqb4Rr5MhKBR3D?si=c1f8a23072464783") |> # Nuvole Bianche by Ludovico Einaudi
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
joep <-
  get_tidy_audio_analysis("55U56qbqS1g1PaeyIznUjr?si=7da1df14c38c4a3f") |> # Midwayer by Joep Beving
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bind_rows(
chopin |>
  compmus_gather_timbre() |>
  mutate(type = "Nocturne by Chopin"),
ludovico |>
  compmus_gather_timbre() |>
  mutate(type = "Nuvole Bianche by Ludovico Einaudi"),
joep |>
  compmus_gather_timbre() |>
  mutate(type = "Midwayer by Joep Beving")
) |>
  mutate() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  facet_wrap(~type) +
  scale_fill_viridis_c() +
  theme_classic() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude")
```

***

Cepstrograms breakdown of the soft classic song by Chopin from research playlist#2.

### Workout

```{r}
blackpink <-
  get_tidy_audio_analysis("0skYUMpS0AcbpjcGsAbRGj?si=1845018d70214865") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
dualipa <-
  get_tidy_audio_analysis("5nujrmhLynf4yMoMtj8AQF?si=bed60c3fbaa548ee") |> # Nuvole Bianche by Ludovico Einaudi
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
lilnasx <-
  get_tidy_audio_analysis("27NovPIUIRrOZoCHxABJwK?si=937f39f001ac48e8") |> # Midwayer by Joep Beving
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bind_rows(
blackpink |>
  compmus_gather_timbre() |>
  mutate(type = "Pink Venom by Blackpink"),
dualipa |>
  compmus_gather_timbre() |>
  mutate(type = "Levitating by Dua Lipa"),
lilnasx |>
  compmus_gather_timbre() |>
  mutate(type = "Industry Baby by Lil Nas X and Jack Harlow")
) |>
  mutate() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value, title(main = 'Lofi - Capturin the Lights')
    )
  ) +
  geom_tile() +
  facet_wrap(~type) +
  scale_fill_viridis_c() +
  theme_classic() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude")
```

***

Cepstrograms breakdown of the pop song "Pink Venom" by Blackpink from research playlist#3.

Self Similarity Matrix {.storyboard data-navmenu=Visualisation}
=========================================

### Lofi

This is chroma and timbre cross analysis of "classical piece"Nocturne in B major Op. 62" by Chopin.

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)

bind_rows(
  lofi1 |>
    compmus_self_similarity(pitches, "aitchison") |>
    mutate(d = d / max(d), type = "Chroma"),
  lofi1 |>
    compmus_self_similarity(timbre, "euclidean") |>
    mutate(d = d / max(d), type = "Timbre")
) |>
  mutate() |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

***

Comment here

### Soft Classical

This is chroma and timbre cross analysis of "classical piece"Nocturne in B major Op. 62" by Chopin.

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)

bind_rows(
  chopin |>
    compmus_self_similarity(pitches, "aitchison") |>
    mutate(d = d / max(d), type = "Chroma"),
  chopin |>
    compmus_self_similarity(timbre, "euclidean") |>
    mutate(d = d / max(d), type = "Timbre")
) |>
  mutate() |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

***

Comment here

### Workout 

This is chroma and timbre cross analysis of "classical piece"Nocturne in B major Op. 62" by Chopin.

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)

bind_rows(
  blackpink |>
    compmus_self_similarity(pitches, "aitchison") |>
    mutate(d = d / max(d), type = "Chroma"),
  blackpink |>
    compmus_self_similarity(timbre, "euclidean") |>
    mutate(d = d / max(d), type = "Timbre")
) |>
  mutate() |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

***

Comment here

Chordograms {.storyboard data-navmenu=Visualisation}
=========================================

### Lofi 
```{r}
circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )

lofi1 |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```


### Soft Classic

```{r, echo=FALSE}
chopin |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

### Workout

```{r}
blackpink |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

Track Level Summaries {.storyboard data-navmenu=Visualisation}
=========================================
### Track Level Summaries 1

```{r}
lofi <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "0vvXsWCC9xrXsKd4FyS8kM?si=33fc00fd735f4afe"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
soft_classical <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "6d7BJsiKHny0PHvgn62pBU?si=3cd9d8cce4d145c5"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
workout <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "37i9dQZF1DX76Wlfdnj7AP?si=c03ee87232224cf8"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
study <-
  lofi |>
  mutate(genre = "Lofi") |>
  bind_rows(workout |> mutate(genre = "Workout"), soft_classical |> mutate(genre = "Soft Classical"))
study |>
  mutate(
    sections =
      map(
        sections,                                    # sections or segments
        summarise_at,
        vars(tempo, loudness, duration),             # features of interest
        list(section_mean = mean, section_sd = sd)   # aggregation functions
      )
  ) |>
  unnest(sections) |>
  ggplot(
    aes(
      x = tempo,
      y = tempo_section_sd,
      colour = genre,
      alpha = loudness
    )
  ) +
  geom_point(aes(size = duration / 60)) +
  geom_rug() +
  theme_minimal() +
  ylim(0, 5) +
  labs(
    x = "Mean Tempo (bpm)",
    y = "SD Tempo",
    colour = "Genre",
    size = "Duration (min)",
    alpha = "Volume (dBFS)"
  )

```

### Track Level Summaries 2

```{r}
chart4 <- study |>
  mutate(
    timbre =
      map(
        segments,
        compmus_summarise,
        timbre,
        method = "mean"
      )
  ) |>
  select(genre, timbre) |>
  compmus_gather_timbre() |>
  ggplot(aes(x = basis, y = value, fill = genre)) +
  geom_violin() +
  scale_fill_viridis_d() +
  labs(x = "Spotify Timbre Coefficients", y = "", fill = "Genre")

ggplotly(chart4)
```

Introduction{.storyboard data-navmenu=Introduction}
=========================================
  
### What features recipe goes into making the best study playlist?
  
```{r}

```

Study playlist can play an important role in the productivity level of any study session. While studying together with friends we ended up in situation where we had to listen to our individual playlists in headphones, because each of our taste in study music was very different. Therefore the first question I want to look into is "What makes any music or song a study-friendly option?". Does it involve its slow rhytm, low dancebility, low energy, low dancebility, yet the most important question I want to figure out is the level of accousticness and instrumentalness across various types of study playlists. My main research question is what combination of the main features classify the music into study friendly. It will be possible to compare the opposite of study music, for example, workout or party playlist and contrast it to study music. 

### Focus playlists 

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/0vvXsWCC9xrXsKd4FyS8kM?utm_source=generator" width="100%" height="352" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/6d7BJsiKHny0PHvgn62pBU?utm_source=generator" width="100%" height="352" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/37i9dQZF1DX76Wlfdnj7AP?utm_source=generator" width="100%" height="352" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>


Conclusion{.storyboard}
=========================================
  
### Conclusion 
  
```{r}

```
